cardinalR: Generating interesting high-dimensional data structures

### 2025-11-07 paper-cardinalR.Rmd
Need to work on rot 2, 3 later

rot2 <- gen_rotation(p = 4, planes_angles = list(
  list(plane = c(1, 3), angle = 30)
))

rot3 <- gen_rotation(p = 4, planes_angles = list(
  list(plane = c(2, 4), angle = 45)
))

# Generate the clustered dataset
clust_data <- gen_multicluster(
  n = c(200, 300, 500),
  k = 3,
  loc = matrix(c(
    0, 0, 0, 0,
    5, 9, 0, 0,
    3, 4, 10, 7
  ), nrow = 3, byrow = TRUE),
  scale = c(3, 1, 2),
  shape = c("gaussian", "cone", "unifcube"),
  rotation = list(rot1, rot2, rot3),
  is_bkg = FALSE
)

>>>>

# Generate the clustered dataset
clust_data <- gen_multicluster(
  n = c(200, 300, 500),
  k = 3,
  loc = matrix(c(
    0, 0, 0, 0,
    5, 9, 0, 0,
    3, 4, 10, 7
  ), nrow = 3, byrow = TRUE),
  scale = c(3, 1, 2),
  shape = c("gaussian", "cone", "unifcube"),
  rotation = list(rot1, NULL, NULL),
  is_bkg = FALSE
)

### 2025-11-07 paper-cardinalR.tex
Need to work on rot 2, 3 later

rot2 <- gen_rotation(p = 4, planes_angles = list(
  list(plane = c(1, 3), angle = 30)
))

rot3 <- gen_rotation(p = 4, planes_angles = list(
  list(plane = c(2, 4), angle = 45)
))

# Generate the clustered dataset
clust_data <- gen_multicluster(
  n = c(200, 300, 500),
  k = 3,
  loc = matrix(c(
    0, 0, 0, 0,
    5, 9, 0, 0,
    3, 4, 10, 7
  ), nrow = 3, byrow = TRUE),
  scale = c(3, 1, 2),
  shape = c("gaussian", "cone", "unifcube"),
  rotation = list(rot1, rot2, rot3),
  is_bkg = FALSE
)
\end{verbatim}

>>>>

# Generate the clustered dataset
clust_data <- gen_multicluster(
  n = c(200, 300, 500),
  k = 3,
  loc = matrix(c(
    0, 0, 0, 0,
    5, 9, 0, 0,
    3, 4, 10, 7
  ), nrow = 3, byrow = TRUE),
  scale = c(3, 1, 2),
  shape = c("gaussian", "cone", "unifcube"),
  rotation = list(rot1, NULL, NULL),
  is_bkg = FALSE
)
\end{verbatim}
